FAIR fission track analysis with geochron@home

### 2025-09-27 geochron@home/manuscript/paper.tex
Created smaller version of the table

The combined data plots of Figures~\ref{fig:AvP}b and c contain two
sets of counts, with $\sum N_{1} = 686$ and $\sum N_{2} = 679$, and a
weighted mean track density ratio $\hat{\rho}_{1}/\hat{\rho}_{1} =
0.94$ with relative standard error 0.013. PV counted 600 tracks in
those common areas $A_0$, of which 549 were also counted by
AC. Conversely, AC counted 622 tracks of which 549 were also counted
by PV. The ratio of the two analysts' track density estimates based
just on the common area is therefore 600/622 = 0.965 with relative
standard error 0.018, calculated from Equation~\ref{eq:NO}. This is
close to the weighted mean ratio of 0.94 (Figure~\ref{fig:AvP}c), and
is slightly nearer to 1. It indicates that PV under-counts the Mount
Dromedary apatite by 3.5\% relative to AC.  The existence of `observer
bias' is well documented \citep{tamer2025}.  It is one of the reasons
why fission track analysis is often done relative to age standards:
observer bias does not have to be a problem provided that it is
consistent between grains, and between samples.\medskip

@@

\noindent\begin{minipage}{.65\linewidth}
\renewcommand{\arraystretch}{0.7}
\begin{scriptsize}
  \input{../output/crowdtable.txt}
\end{scriptsize}
\end{minipage}
\begin{minipage}{.35\linewidth}
\captionof{table}{Summary table of the crowd sourcing results for the
  different users (rows) and grains (columns).  The last row is the
  ratio of the median count to PV's count for each grain.  The last
  column is the ratio of the pooled count over grains compared with PV
  for the same grains.}
\label{tab:crowdtable}
\end{minipage}

%\begin{figure}[!ht]
{ \centering \includegraphics[width=15cm]{23vs25.pdf}
  \captionof{figure}{ a) The track counts for grain~25 plotted against
    those for grain~23 for 37 students who counted both of those
    grains. b) Optical images in transmitted light of Mount Dromedary
    apatites 23 and 25 in the crowd-sourcing experiment, along with
    two-dimensional histogram of the track locations for the two
    grains, as identified by the citizen scientists.
    \medskip}
  \label{fig:23vs25}
}%\end{figure}

>>>>

The combined data plots of Figures~\ref{fig:AvP}b and c contain two
sets of counts, with $\sum N_{1} = 686$ and $\sum N_{2} = 679$, and a
weighted mean track density ratio $\hat{\rho}_{1}/\hat{\rho}_{1} =
0.94$ with relative standard error 0.013. PV counted 600 tracks in
those common areas $A_0$, of which 549 were also counted by
AC. Conversely, AC counted 622 tracks of which 549 were also counted
by PV. The ratio of the two analysts' track density estimates based
just on the common area is therefore 600/622 = 0.965 with relative
standard error 0.018, calculated from Equation~\ref{eq:NO}, with $N_1
= 686$, $N_2 = 679$ and $N_0 = 549$.  This is close to the weighted
mean ratio of 0.94 (Figure~\ref{fig:AvP}c), and is slightly nearer to
1. It indicates that PV under-counts the Mount Dromedary apatite by
3.5\% relative to AC.  The existence of `observer bias' is well
documented \citep{tamer2025}.  It is one of the reasons why fission
track analysis is often done relative to age standards: observer bias
does not have to be a problem provided that it is consistent between
grains, and between samples.\medskip

@@

\begin{small}
  \input{../output/shortcrowdtable.txt}\\
\end{small}
\captionof{table}{Counts of fission tracks in the same ROIs of 25
  grains made by PV and 68 students. Only 20 grains and 20 students
  are shown due to space constraints; the full table is provided in
  the supplementary information.  Each student counted a subset of the
  grains. The grains are listed in increasing order of PV's
  counts. The last 3 columns give, for each student, the number of
  grains counted $n_g$ and the weighted mean $r_p =
  \sum\,w_i\,r_i/\sum\,w_i$ and standard deviation $s_p =
  \sqrt{w_i\,(r_i-r_p)^2/(n_g − 1)}$ where $r_i$ is the ratio of the
  student's count to PV's count for grain $i$ and $w_i$ is PV's count
  for grain $i$. ($r_p$ is the same as the ratio of the student's
  total count over the $n_g$ grains to PV's total count over the same
  grains.)  The students are listed in decreasing order of $r_p$ . The
  last 3 rows ($n$, $\bar{y}$ and $s_y$ ) give the sample size (number
  of students), mean and standard deviation of the students' counts
  for each grain.}
\label{tab:crowdtable}
%\end{minipage}

%\begin{figure}[!ht]
{ \centering \includegraphics[width=15cm]{23vs25.pdf}
  \captionof{figure}{a) The track counts for grain~23 plotted against
    those for grain 25 for 36 students who counted both of those
    grains. The grey line through the origin has slope equal to the
    ratio of the total counts for each grain. The blue dot shows PV's
    counts for those two grains. b) Optical images in transmitted
    light of Mount Dromedary apatites 23 and 25 in the crowd-sourcing
    experiment, along with two-dimensional histogram of the track
    locations for the two grains, as identified by the citizen
    scientists.
    \medskip}
  \label{fig:23vs25}
}%\end{figure}
